---
title: "music p2"
output:
  html_document:
    df_print: paged
---
## Since sourcing isn't working to knit this I will include the specific data I need
### Which is probably most of it

```{r setup, include=FALSE}
suppressMessages(library("tidyverse"))
suppressMessages(library("knitr"))

#setwd("B:/Documents/MATH314/385/musicsurvey/")
#purl("insight.Rmd", output = "part1.r")
#source("B:/Documents/MATH314/385/musicsurvey/part1.r")

suppressMessages(surv <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv"))
suppressMessages(pref <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv"))
```

```{r}
colnames(surv)[colnames(surv) == "Timestamp"] <- "time_sub"
colnames(pref)[colnames(pref) == "Timestamp"] <- "time_sub"
colnames(surv)[colnames(surv) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "generator"
colnames(surv)[colnames(surv) == "What is your pseudonym?"] <- "name"
colnames(pref)[colnames(pref) == "What was your pseudonym?"] <- "name"
colnames(surv)[colnames(surv) == "Sex"] <- "sex"
colnames(surv)[colnames(surv) == "Major"] <- "major"
colnames(surv)[colnames(surv) == "Academic Year"] <- "grade_level"
colnames(surv)[colnames(surv) == "Year you were born (YYYY)"] <- "year_born"
colnames(surv)[colnames(surv) == "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument"
colnames(surv)[colnames(surv) == "Artist"] <- "song_artist"
colnames(surv)[colnames(surv) == "Song"] <- "song"
colnames(surv)[colnames(surv) == "Link to song (on Youtube or Vimeo)"] <- "link"

people <- tibble(generator = surv$generator, name = surv$name, sex = surv$sex, major = surv$major, grade_level = surv$grade_level, year_born = surv$year_born, instrument = surv$instrument, time = surv$time_sub)

people$time <- as.POSIXlt(parse_datetime(people$time, format = "%D %H:%M"))

N <- nrow(surv)
for(n in 1:N) {
  if(identical(x = people$generator[n], y ="Fake rapper name generator")) {   
    people$generator[n] <- "rapper"
  } else {
    people$generator[n] <- "band"
  }
}


#install.packages("pracma")
suppressMessages(library("pracma"))
for(n in 1:N) {
  for(z in 1:N) {
    if(strcmpi(people$major[n], people$major[z])) {
      people$major[z] = people$major[n]
    }
  }
}
suppressMessages(detach("package:pracma", unload=TRUE))

people$major <- as.factor(people$major)

```

## I will be taking the average score of what each person gave to the songs.

Going to split the data into a 25% testing set and a 75% training set.

```{r}
#Removing the duplicate names first turn in
updatePref <- pref[-18,]
updatePref <- updatePref[-37,]

meanRat <- rowMeans(updatePref[,3:45])

averageTib <- tibble(gen = people$generator, name = people$name, sex = people$sex, major = people$major, grade = people$grade_level, year = people$year_born, average = meanRat)

averageTib <- drop_na(averageTib)

#install.packages("caret")
suppressMessages(library(caret))

# Split the data into training and test set
set.seed(123)
training.samples <- averageTib$average %>%
  createDataPartition(p = 0.75, list = FALSE)
train.data  <- averageTib[training.samples, ]
test.data <- averageTib[-training.samples, ]
# Build the model
model <- lm(average ~.-name, data = train.data)

summary(model)
```


## Results

While it appears nothing was specifically statistically significant the closest to significants was the choice of generator being rapper.